\chapter{Conclusion}
\label{conclusion}

In~this work, a research was done into~popular object detection methods and a summary was made. Special attention was paid to~the evolution of~YOLO algorithm where each version until the most recent one at the time of writing the thesis was described. Particular detail was given to the current state-of-the-art YOLOv7. Moreover, datasets for~keyboard detection, single-character detection and post-processing were devised and created. These datasets were used for~training and validation of~the recognition methods. The datasets are unique as~no other is to~the best of~my knowledge publicly available. They can serve not only the~keyboard typing automation task but also any other which might use keyboard detection or single-character detection. Then, a three-phased image processing strategy was designed and implemented. Firstly, YOLOv7 neural network model is used for~keyboard detection. Secondly, characters are recognized in~the detected keyboard region again using YOLOv7. The found characters symbolize potential keys and are further processed in~the last stage. The post-processing algorithm corrects mistakes based on~predefined supported layouts. Furthermore, it can be easily extended to~handle new scenarios. The results of~each phase were evaluated and found satisfactory. The accuracy of the methods exceeds expectations, particularly keyboard detection and recognition of~alphanumeric characters. Consequently, a novel modular solution for~keyboard and keys recognition was created which can be effortlessly extended or its parts replaced. This solution is to~be used in~the production environment of~Y~Soft~AIVA system where it will help with automating robotic keyboard typing. On~top of~that, the thesis received Jiří Kunovský award from Excel@FIT~2023 conference based on~votes from the professional public.

In~future work, the actual integration into~the AIVA system needs to~be done. Other than that, there is room for~improvement with respect to~special characters' accuracy. Moreover, additional character sets can be supported such as other alphabets, diacritics or more \hbox{special} characters. The same holds for~support of~new keyboard layouts. Also, as~new state-of-the-art detectors will be emerging, the models can get retrained to~improve the overall results.



